\begin{thebibliography}{99}
\item[]\textbf{Tiếng Việt}
\bibitem{1}Đoàn Trí Dũng, \textit{Động học của polariton trong bán dẫn microcavity, Luận văn Cao học Vật lý lý thuyết}, Trường Đại học Khoa Học Tự Nhiên, TP. Hồ Chí Minh(2005).
\bibitem{2}Vũ Quan Tuyên vs Khóa 08 (2012), \textit{Project nhóm phương trình  Bloch },Vật lý tính toán, Trường Đại học Khoa Học Tự Nhiên, TP. Hồ Chí Minh.
\bibitem{3} Hoàng Dũng, \textit{Bài tập Cơ Học Lượng Tử },Nhà xuất bản ĐHQG, TP. Hồ Chí Minh,(2000) p 141,142
\bibitem{4} N. H. Chí, \textit{Điện động lực học},Nhà xuất bản ĐHQG, TP. Hồ Chí Minh, (2001)p 105,106
\item[]\textbf{Tiếng Anh}
\bibitem{5}Nakamura, Science, 281, (1998), 956; IEEE, \textit{ Circuits and Devices}, May, 19 (1995)
\bibitem{6}P. Marconcini and M. Macucci, \textit{The k · p method and its application to graphene, carbon nanotubes and graphene nanoribbons: the Dirac equation}, DOI 10.1393/ncr/i2011-10068-1.
\bibitem{7}L. Esaki, L.L. Chang and R. Tsu, \textit{Proceedings 12th International
Conference on Low Temperature Physics},Kyoto, Japan, September
1970. (Keigaku Publishing Co., Tokyo, Japan) 551.
\bibitem{8}F.Schubert,\textit{Rensselaer Polytechnique Institute}, 2003.
\bibitem{9}J.J Sakurai, \textit{Modern Quantum Mechanics},revised edn. (Addison-Wesley, Red-wood City, 1994) 31, 83, 151, 152, 185, 204, 208
\bibitem{10}P.O. L$\ddot{o}$din: J. Chem. Phys. 19(11), 1396–1401 (1951) 201
\bibitem{11}J.M. Luttinger, W. Kohn: Phys. Rev. 97(4), 869–883 (1955) 3, 38, 201
\bibitem{12}G.L. Bir, G.E. Pikus, \textit{Symmetry and Strain-Induced Effects in Semiconductors}, (Wiley, New York, 1974) 3, 4, 6, 15, 16, 18, 19, 98, 118, 213, 201
\bibitem{13}B. Pasenow, H. T. Duc, T. Meier, and S. W. Koch, 
\textit{Solid State Commun}, 145,61 (2008).
\bibitem{14}M. Bieler, K. Pierz, U. Siegner, P. Dawson, H. T. Duc, J. F$\ddot{o}$rst$-$ner, and T. Meier, Proc
\textbf{SPIE} 7214, 721404 (2009)
\bibitem{15}H. Deng, G. Weihs, C. Santori, J. Bloch, and Y. Yamamoto, \textit{Semiconductor Optics and Trans-port Phenomena},Springer, Berlin (2003).
\bibitem{16}H.T. Duc, J. F$\ddot{o}$rstner, T. Meier,
\textit{Microscopic analysis of charge and spin photocurrents injected by circularly polarized one-color laser pulses in GaAs quantum wells}, Rev. B 82,115316 (2010)
\bibitem{17}H. Haug and S. W.Koch, \textit{Qantum theory of the optical and electronic problem semiconductor,2nd ed},Word Scientific, Singapore (1993)
\bibitem{18}N. Peyghambarian, S. W. Koch and A. Mysyrowwicz, \textit{Introduction to Semiconductor Optics} (1995) p,115,116
\bibitem{19}Michael Pfeiffer, \textit{Diploma Thesis at the Department of Information Technology and Electrical Engineering}, ETH.
\bibitem{20}M. Kira, F. Jahnke, W. Hoyer, S.W. Koch, \textit{Quantum theory of spontaneous emission and coherent e!ects in semiconductor
microstructures}, elsevier.com(1999)
\bibitem{21}G.F. Koster, J.O. Dimmock, R.G. Wheeler, H. Statz, \textit{Properties of the Thirty-Two Point Groups}, MIT, Cambridge, MA, (1963)
\bibitem{22} Dr. Roland Winkler \textit{Spin–Orbit Coupling Effects
in Two-Dimensional Electron and Hole Systems}, Springer (2003)
\bibitem{23} SHUN LIEN CMUANG \textit{Physics of Optoelectronic Devices}, Wiley Series Pure and Applied Optics (1995)
\bibitem{24}H. D. Duc, \textit{The kp menthod semiconductor },(2010).
\bibitem{25} PAUL HARRISON, \textit{Quantum Wells,Wries and Dots} Wiley (2005).
\bibitem{26} F.Schubert, \textit{Rensselaer Polytechnique Institut}  (2003).

\end{thebibliography}